---
title: Exploring PhramaRTF
author: Ben Straub
date: '2021-03-17'
slug: phramartf
categories:
  - Clinical Reporting
  - Demo
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-03-17T16:46:43-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


Welcome 👋 We know that first impressions are important, so we've populated your new site with some initial content to help you get familiar with everything in no time.  Welcome 👋 We know that first impressions are important, so we've populated your new site with some initial content to help you get familiar with everything in no time.  Welcome 👋 We know that first impressions are important, so we've populated your new site with some initial content to help you get familiar with everything in no time.

```{r}
#install.packages("pharmaRTF")
#install.packages("dplyr")
library(pharmaRTF)
library(dplyr)

```


```{r}
dat <- iris %>% 
  select(Species, everything())

ht <- huxtable::as_hux(dat, add_colnames=TRUE) %>% 
  huxtable::set_bold(1, 1:ncol(dat), TRUE) %>% 
  huxtable::set_bottom_border(1, 1:ncol(dat), 1) %>% 
  huxtable::set_width(1.5)
ht[1:10,]

```


```{r}

doc <- rtf_doc(ht, titles=list(hf_line("The Iris Dataset", bold=TRUE)))

#write_rtf(doc, file="table1.rtf")

```